The \textit{Kepler} Smear Campaign: Light curves for 102 Very Bright Stars

### 2019-05-17 paper/ms.tex
new figures

\begin{figure*}
\plotone{Pope_alpha_oddZ.pdf}

\caption{\label{alphael}
The [Mg/Fe], [Si/Fe], [Ti/Fe], [V/Fe] (left panel) and [Al/Fe], [Ca/Fe], [Ni/Fe], [Cr/Fe] (right panel) abundance ratios as a function of iron for our stars (black circles). We also show a representative sample of Galactic disk stars from \citet[open red squares]{Bensby2014}, \citet[open orange squares]{Adibekyan2012}, and \citet[light green circles]{Battistini2015}. These elemental ratios show that the chemical composition of our sample is consistent with the Galactic disk population. } %Mg was chosen as an illustrative $\alpha$-element. } 
\end{figure*}

@@

In addition, to the $\alpha$ and odd-Z elements we also derived the chemical abundance for several neutron capture elements including Sr, Zr, La, Eu (left panel of Fig~\ref{fig:ncap}) as well as Y, Ba, and Nd (right panel of Fig.~\ref{fig:ncap}).  It is clear from Fig.~\ref{fig:ncap}  that the chemical abundance ratio of each neutron capture element is consistent with the Galactic disk population. The Ba of our sample is slightly enhanced, however, while the Y of our sample is slightly reduced relative to the general disk population of \cite{Bensby2014}. Nevertheless, we conclude all elemental abundance ratios studied our sample most closely resemble the Galactic disk. 
\begin{figure*}
\plotone{Pope_ncap.pdf}

\caption{\label{fig:ncap}
The [Mg/Fe], [Si/Fe], [Ti/Fe], [V/Fe] (left panel) and [Al/Fe], [Ca/Fe], [Ni/Fe], [Cr/Fe] (right panel) abundance ratios as a function of iron for our stars (black circles). We also show a representative sample of Galactic disk stars from \citet[open red square,][]{Bensby2014}, \citet[green circles][]{Battistini2016}. These elemental ratios give a representive example of the chemical composition of our sample and show they are consistent with the Galactic disk population. } %Mg was chosen as an illustrative $\alpha$-element. } 
\end{figure*}

>>>>

\begin{figure*}
\plotone{Pope_Fig7_v1.pdf}

\caption{\label{alphael}
The [Mg/Fe], [Si/Fe], [Ti/Fe], [V/Fe] (left panel) and [Al/Fe], [Ca/Fe], [Ni/Fe], [Cr/Fe] (right panel) abundance ratios as a function of iron for our stars (black circles). We also show a representative sample of Galactic disk stars from \citet[open red squares]{Bensby2014}, \citet[open blue squares]{Adibekyan2012}, and \citet[teal circles]{Battistini2015}. These elemental ratios show that the chemical composition of our sample is consistent with the Galactic disk population. } %Mg was chosen as an illustrative $\alpha$-element. } 
\end{figure*}

@@

In addition, to the $\alpha$ and odd-Z elements we also derived the chemical abundance for several neutron capture elements including Sr, Zr, La, Eu (left panel of Fig~\ref{fig:ncap}) as well as Y, Ba, and Nd (right panel of Fig.~\ref{fig:ncap}).  It is clear from Fig.~\ref{fig:ncap}  that the chemical abundance ratio of each neutron capture element is consistent with the Galactic disk population. The Ba of our sample is slightly enhanced, however, while the Y of our sample is slightly reduced relative to the general disk population of \cite{Bensby2014}. Nevertheless, we conclude all elemental abundance ratios studied our sample most closely resemble the Galactic disk.

\begin{figure*}
\plotone{Pope_Fig8_v1.pdf}
\caption{\label{fig:ncap}
The [Mg/Fe], [Si/Fe], [Ti/Fe], [V/Fe] (left panel) and [Al/Fe], [Ca/Fe], [Ni/Fe], [Cr/Fe] (right panel) abundance ratios as a function of iron for our stars (black circles). We also show a representative sample of Galactic disk stars from \citet[open red square,][]{Bensby2014}, \citet[blue circles][]{Battistini2016}. These elemental ratios give a representive example of the chemical composition of our sample and show they are consistent with the Galactic disk population. } %Mg was chosen as an illustrative $\alpha$-element. } 
\end{figure*}
